Compare pseqs

### 2019-05-29 comparepseqs.Rmd
Typo, split model function

    if (!file.exists(paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))) {
        missing$alphadistribution = TRUE
    } else {
        alphadiversity <- readRDS(file = paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))
    }

@@

    if (!file.exists(paste0("rds-comparepseqs/beta-", key , ".rds"))) {
        missing$beta = TRUE
    } else {
        betadiversity <- readRDS(file = paste0("rds-comparepseqs/beta-", key , ".rds"))
    }

    if (length(missing) > 0) {
        pseq <- import_filter_data(rds[[key]])
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = as.numeric(scale(diversities_shannon)))

@@

        if ("beta" %in% names(missing)) {
            message("Missing beta")
            betadiversity <- list(min = calculateadonis(dset = dset,
                                                        matrix = bray.dist.matrix,
                                                        covariates = covariates.min,
                                                        npermutations = 1000),
                                  full = calculateadonis(dset = dset,
                                                         matrix = bray.dist.matrix,
                                                         covariates = covariates.full,
                                                         npermutations = 1000))
            saveRDS(betadiversity, file = paste0("rds-comparepseqs/beta-", key , ".rds"))
        }
    }

    ret[[key]] = list("alphadiversity" = alphadiversity,
                      "betadiversity" = betadiversity,
                      "alphadistribution" = alphadistribution)
}
```

>>>>

    if (!file.exists(paste0("rds-comparepseqs/alphadistribution-", key , ".rds"))) {
        missing$alphadistribution = TRUE
    } else {
        alphadistribution <- readRDS(file =
                                         paste0("rds-comparepseqs/alphadistribution-",
                                                key , ".rds"))
    }

@@

    if (!file.exists(paste0("rds-comparepseqs/beta-", key , ".rds"))) {
        missing$beta = TRUE
    } else {
        betadiversity <- readRDS(file = paste0("rds-comparepseqs/beta-", key , ".rds"))
    }
}
```

```{r calculate missing models}
if (length(missing) > 0) {
    for (key in names(rds)) {
        pseq <- import_filter_data(rds[[key]],
                                   included = c("MEN", "BL_AGE", "SYSTM", "DIASM", "BMI",
                                                "CURR_SMOKE", "BL_USE_RX_C09",
                                                "Q57X", "BL_USE_RX_C03",
                                                "BL_USE_RX_C07", "BL_USE_RX_C08"))
        dset <- meta.merge.alphadiversity(pseq) %>%
            mutate(diversities_shannon = as.numeric(scale(diversities_shannon)))

@@

        if ("beta" %in% names(missing)) {
            message("Missing beta")
            betadiversity <- list(min = calculateadonis(dset = dset,
                                                        matrix = bray.dist.matrix,
                                                        covariates = covariates.min,
                                                        npermutations = 1000),
                                  full = calculateadonis(dset = dset,
                                                         matrix = bray.dist.matrix,
                                                         covariates = covariates.full,
                                                         npermutations = 1000))
            saveRDS(betadiversity, file = paste0("rds-comparepseqs/beta-", key , ".rds"))
        }

        ret[[key]] = list("alphadiversity" = alphadiversity,
                          "betadiversity" = betadiversity,
                          "alphadistribution" = alphadistribution)
    }
}
```
